\Large \bf Conjure: Summoning Proxies from Unused Address Space

### 2019-05-16 paper/paper.tex
add applications table
minor edits

To register, clients connect to a \textbf{decoy} site that supports TLS. They
complete the handshake, and send a normal HTTPS request that embeds a special
steganographic \textbf{tag} in the ciphertext of the request. We use
the same technique used in TapDance's covert ciphertext
channel\footnote{Section~3 in
TapDance~\cite{tapdance14}} to embed the tag, but we purposefully have the client
send a complete request (rather than incomplete), allowing the decoy server to respond.
The steganographic tag is only visible to the ISP station, which can see the tag using its
private key. Unlike in TapDance, the \scheme station can passively observe
the tag, and does not need to respond to it (which requires mimicking the
decoy).
%In addition, more potential decoys can be used than in TapDance, as
%there is no need to exclude decoys that have timeouts or TCP windows unfavorable
%for keeping connections open. We estimate in our deployment an increase of 25\%
%in decoys that could be used.

@@

Any protocol that satisfies these criteria can be used as an application. In
this section, we describe existing protocols (obfs4 and obfuscated SSH) as well
as introduce our own (Mask sites, TLS 1.3 eSNI, and phantom WebRTC clients) that
can be used in \scheme, and evaluate how each meet the necessary requirements.
Figure~\ref{fig:overview} describes a high-level overview of the \scheme
registration and application behavior.

@@

Obfuscated SSH~\cite{ossh} is a protocol that attempts to mask the Secure Shell
(SSH) protocol in a thin
layer of encryption. This makes it difficult for censors to identify using basic
packet filters, as there are no identifying headers or fields
to search for. Instead, Obfuscated SSH clients first send a 16-byte seed, which
is then used to derive a symmetric key that encrypts the rest of the
communication. While this can passively detected by censors (who can also
derive the key and deobfuscate the protocol), the key derivation is deliberately
slowed by an iterated hash to make such identifcation
expensive (though not impossible) at high speeds.

Obfuscated SSH also does not protect against active probing, as the censor can
easily create their own connections and confirm the server is using the
protocol. Nonetheless, this protocol is still used successfully in deployed censorship
circumvention systems~\cite{psiphon}. Obfuscated SSH can also be used as a \scheme
application protocol, though we note it provides no active probing or passive
identifcation resistance.

@@

@@

Phantom host IP addresses must be derived from network blocks that are routed (so they pass
the ISP station) and contain other legitimate hosts (so that censors cannot
block the entire network without collateral damage).
Because of the large number of IPv6 addresses, even
relatively small network prefixes have astronomical numbers of addresses: a
single /32 prefix has $2^{96}$ possible addresses. Therefore, client-chosen
seeds have negligible probability of corresponding to addresses that are already
being used by legitimate hosts. This allows us to select phantom host addresses
from network prefixes that contain
legitimate hosts---crucial to discouraging the censor from blocking them
outright---without worry that registrations could interfere with legitimate
services.

>>>>

To register, clients connect to a \textbf{decoy} site that supports TLS. They
complete the handshake, and send a normal HTTPS request that embeds a special
steganographic \textbf{tag} in the ciphertext of the request. We use
the same technique used in TapDance's covert ciphertext
channel~\cite[\S3]{tapdance14}
to embed the tag, but we purposefully have the client
send a complete request (rather than incomplete), allowing the decoy server to respond.
The steganographic tag is only visible to the ISP station, which can see the tag using its
private key. Unlike in TapDance, the \scheme station can passively observe
the tag, and does not need to respond to it, obviating the need to mimick the decoy.
In addition, more potential decoys can be used than in TapDance, as
there is no need to exclude decoys that have timeouts or TCP windows unfavorable
for keeping connections open. In our ISP deployment, this results in a modest increase
of 25\% more decoys that could be used than in TapDance.

@@

Any protocol that satisfies these criteria can be used as an application. In
this section, we describe existing protocols (obfs4 and obfuscated SSH) as well
as introduce our own (Mask sites, TLS 1.3 eSNI, and phantom WebRTC clients) that
can be used in \scheme, and evaluate how each meet the necessary requirements.
Figure~\ref{fig:overview} describes a high-level overview of the \scheme
registration and application behavior, and Table~\ref{tab:applications} compares the
application protocols.

@@

Obfuscated SSH~\cite{ossh} (OSSH) is a protocol that attempts to mask the Secure Shell
(SSH) protocol in a thin
layer of encryption. This makes it difficult for censors to identify using basic
packet filters, as there are no identifying headers or fields
to search for. Instead, Obfuscated SSH clients first send a 16-byte seed, which
is then used to derive a symmetric key that encrypts the rest of the
communication. While this can passively detected by censors (who can also
derive the key and de-obfuscate the protocol), the key derivation is deliberately
slowed by an iterated hash to make such identification
expensive (though not impossible) at high speeds.

Obfuscated SSH also does not protect against active probing, as the censor can
easily create their own connections and confirm the server is using the
protocol. Nonetheless, this protocol is still used in deployed censorship
circumvention systems~\cite{psiphon}, though has to deploy proxies at new IP
addresses when censors inevitably discover and block them.
Obfuscated SSH can also be used as a \scheme
application protocol, though we note it provides no active probing or passive
identification resistance. However, \scheme OSSH can still make it cheaper to
rotate to new IP addresses when proxies are found and blocked.

@@

\TabApplications

@@

Phantom host IP addresses must be derived from network blocks that are routed (so they pass
the ISP station) and contain other legitimate hosts (so that censors cannot
block the entire network without collateral damage).
Because of the large number of IPv6 addresses, even
moderately-sized network prefixes have astronomical numbers of addresses: a
single /32 prefix has $2^{96}$ possible addresses. Therefore, client-chosen
seeds have negligible probability of corresponding to addresses that are already
being used by legitimate hosts. This allows us to select phantom host addresses
from network prefixes that contain
legitimate hosts---crucial to discouraging the censor from blocking them
outright---without worry that registrations could interfere with legitimate
services.
